---
title: "{flexdashboards}"
subtitle: "Data visuals. On a board."
author: "Akhila Nekkanti"
date: "Winter 2021"
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      
---
class: center, left

```{r setup, include = FALSE}

knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
library(tidyverse)
library(here)
library(rio)
library(dplyr)
library(likert)
library(colorblindr)
library(ggridges)
library(scales)
library(fmsb)
theme_set(theme_minimal(15))
#[metropolis, metropolis-fonts]

```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_mono_light(
  base_color = "#ef8b43",
  header_font_google = google_font("Josefin Sans"),
  text_font_google   = google_font("Montserrat", "300", "300i"),
  code_font_google   = google_font("Fira Mono")
)
```


## Policymakers rely on publically available, easily digestible data to allocate funds and resources. It is critical then, that such data is accurate. 

--


In Oregon these data are dependent on either retrospective surveys with adults (Oregon BRFFS), youth convenience sample surveys with fewer than 10 abuse and neglect items (Oregon Healthy Teens Survey, Oregon Student Wellness Survey), and reports to child protective services (Children’s Bureau, 2019). 


---
class: left, middle

**To get a better picture of how abuse and neglect rates in Lane County look, the OCAP study directly asks high school students about their current and previous abuse and harrassment experiences.**

I will present three plots that visualize data in informative ways for policymakers. 

--
1. How abuse rates vary across school districts in Lane County.

--
2. How people in the community respond when students have disclosed their experience. 

--
3. How being in foster care is associated with students' decision to tell someone, relative to their abuse score. 

---
class: center, middle

Plot 1.1

```{r plot1.1, echo=FALSE, tidy=FALSE}
#here i'm trying to visualize how many of those who have experienced abuse have told someone about it. And whether this varies by school district. 

```
---
class: center, middle

Plot 1.2
```{r plot1.2, echo=FALSE, tidy=FALSE}


```



---
class: center, middle

Plot 1.3
```{r echo=FALSE, tidy=FALSE}



```


```{r echo=FALSE, tidy=FALSE}
# ggplot(p, aes(x = PATOTR, y = district)) + 
#   geom_density_ridges(aes(fill = Q162),alpha = 0.7) +
#   scale_fill_OkabeIto() +
#   	labs(y = NULL,
# 	     x = "Told someone?",
# 	     title = "Distribution of Abuse Rates",
# 	     subtitle = "Results displayed by disclosure and school district",
# 	     fill = NULL) 


```

```{r echo=FALSE, tidy=FALSE}
# ggplot(p, aes(as.factor(Q162), PATOTR)) +
# 	geom_col(aes(fill = Q162), size = 1) +
# #   geom_violin(aes(color = Q162)) +
#   facet_wrap(~district, ncol = 5) +
#   scale_fill_OkabeIto()+
# 	labs(y = "Physical Abuse Scores",
# 	     x = "Told someone?",
# 	     title = "Distribution of Abuse Rates",
# 	     subtitle = "Results displayed by disclosure and school district",
# 	     fill = NULL) 

```

---
class: center, middle

Plot 2.1
```{r plot2.1, include=FALSE, tidy=FALSE}



```


```{r likertdata, echo=FALSE, tidy = TRUE}


```
---
class: center, middle
Plot 2.2
```{r likert1, echo=FALSE}




```


---
class: center, middle

Plot 2.2

```{r likert2}


```
---
class: middle, center

Plot2.3
```{r likert3}



```


---
class: center, middle

Plot3.1
```{r echo=FALSE}


# ods %>%
#   filter(Q28 == "Strongly Agree" |
#            Q28 == "Strongly Disagree" |
#            Q28 == "Disagree" |
#            Q28 == "Agree") %>% 
#   mutate(adults = fct_recode(Q28,
#                              "Yes" = 'Strongly Agree',
#                              "Yes" = 'Agree',
#                              "No" = 'Strongly Disagree',
#                              "No" = 'Disagree')) %>% 
# ggplot(aes(district, as.factor(adults))) +
#     geom_tile(aes(fill = PATOTR)) +
#   scale_fill_viridis_c() +
#   labs(
#     fill = "Physical Abuse Score",
#     x = NULL,
#     y = NULL,
#     title = "Abuse Scores Vary by Perceived Safe Adults and District"
#   ) +
#   theme(
#     legend.position = "bottom"
#   )


```

```{r include=FALSE}



```


```{r plot3.1}



```
---
class: center, middle

Plot 3.2
```{r plot3.2}


```
---
class:center, middle
Plot 3.3
```{r}


```


  


  
```

---
class: center, middle

# Thanks!

Slides created via the R package [**xaringan**](https://github.com/yihui/xaringan).

The chakra comes from [remark.js](https://remarkjs.com), [**knitr**](http://yihui.org/knitr), and [R Markdown](https://rmarkdown.rstudio.com).
